Home

### 2020-03-25 analysis/index.Rmd
gemma
v1.0 simulate expression using separate data 20191127
polygenic done
fix results display bug

---
title: "Home"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---

## [Model](model.html)

## [Simulation](simulation-singleG.html)

>>>>

---
title: "Home"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
editor_options:
  chunk_output_type: console
---

# Model
  [polygenic model](polygenic_model.html)

# Simulations

## For a single gene
  * [single gene](simulation-singleG.html)

## Under polygenic model
  * [Simulation: WTCCC](simulation-WTCCC.html)
  * [Simulation: WTCCC 2](simulation-WTCCC2.html)
